---
title: "RMER_November2018_Traits"
author: "joellarwood"
date: "2019-12-13"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

## Introduction

```{r echo = FALSE, warnings = FALSE, message=FALSE}
library(tidyverse)
library(lmerTest)
library(emmeans)
library(sjPlot)
library(apa)
library(interactions)
library(glmmLasso)

knitr::opts_chunk$set(autodep = TRUE, warnings = FALSE, message = FALSE)

options(scipen=999, digits=3)
```

## Read in and make long form 
```{r ReadIn}
Nov18BasicClean <- read_rds(here::here("data", "RMER_November2018_ProcessedWide.rds"))

Nov18WorkingLong <- Nov18BasicClean  %>% 
  select(ResponseId, 
         Baseline:rumination) %>% 
  pivot_longer(cols = Baseline:PostListening, 
               names_to = "Timepoint", 
               names_ptypes = factor(), 
               values_to = "Sadness") # %>% 
 # as_factor(Timepoint)

Nov18WorkingLong$Timepoint <- fct_relevel(Nov18WorkingLong$Timepoint, 
                                          "PostInduction") # Not sure why factor conversion is not woring in pipe


```

# Write data
```{r WriteLong}
Nov18WorkingLong %>% 
  write_rds(here::here("data", "RMER_November2018_Processedlong.rds"))

Nov18WorkingLong %>% 
  write_csv(here::here("data", "RMER_November2018_Processedlong.csv"))
```


## Model data 
### Manipulation check 

The induction of sadnes was succesfull `r apa::t_apa(t_test(Nov18BasicClean$Baseline, Nov18BasicClean$PostInduction, paired = TRUE), format = "markdown")`

## Confirmatory Analysis
```{r ConfirmGLMM}

PostInductionTimePoints <- lmerTest::lmer(Sadness~1 + Timepoint  + rumination + Timepoint:rumination + (1|ResponseId), data = filter(Nov18WorkingLong, Timepoint != "Baseline"))

sjPlot::tab_model(PostInductionTimePoints, 
                  show.std = TRUE, 
                  show.aic = TRUE,
                  show.df = TRUE
                  )
```

There was a mean difference however, `r apa::t_apa(t_test(Nov18BasicClean$PostListening, Nov18BasicClean$PostInduction, paired = TRUE), format = "markdown")`

```{r ConfirmInteraction}
lmerTest::difflsmeans(PostInductionTimePoints)

minrum <- mean(Nov18BasicClean$rumination, na.rm = TRUE) - sd(Nov18Working$rumination, na.rm = TRUE)
meanrum <- mean(Nov18BasicClean$rumination, na.rm = TRUE)
plusrum <- mean(Nov18BasicClean$rumination, na.rm = TRUE) + sd(Nov18Working$rumination, na.rm = TRUE)


emmeans::contrast(emmeans::emmeans(PostInductionTimePoints, 
                                   ~rumination*Timepoint, 
                                   at = (list(rumination = c(minrum, plusrum, meanrum), Timepoint = c("PostInduction", "PostListening")))), 
                  "pairwise", 
                  by = "rumination")
```

Value of slope at lowest possible rumination score 

```{r}
emmeans::contrast(emmeans::emmeans(PostInductionTimePoints, 
                                   ~rumination*Timepoint, 
                                   at = (list(rumination = c(3), Timepoint = c("PostInduction", "PostListening")))), 
                  "pairwise", 
                  by = "rumination")
```

#Johnson Neyman 
```{r}
DummyLong <- Nov18WorkingLong %>% 
  filter(Timepoint != "Baseline") %>% 
  mutate(Dummy = if_else(Timepoint == "PostInduction", 0, 1))

DummyGLMM <- lmerTest::lmer(Sadness~1 + Dummy  + rumination + Dummy:rumination + (1|ResponseId), data = DummyLong)

sjPlot::tab_model(DummyGLMM)

upperJN <- interactions::johnson_neyman(model = DummyGLMM, 
                             pred = "Dummy", 
                             modx = "rumination")$bounds[[2]]

emmeans::contrast(emmeans::emmeans(PostInductionTimePoints, 
                                   ~rumination*Timepoint, 
                                   at = (list(rumination = c(upperJN, 1), Timepoint = c("PostInduction", "PostListening")))), 
                  "pairwise", 
                  by = "rumination")


quantile(Nov18BasicClean$rumination, c(.05, .06, .07, .08), na.rm = TRUE)

```

The JN interval was `r round(upperJN, 2)` this score is representative of the `r percentile()`

```{r PlotConfirm}
confirm_plot <- emmeans::emmip(emmeans::ref_grid(PostInductionTimePoints, 
                                 list(rumination = c(plusrum, meanrum, minrum), Timepoint = c("PostInduction", "PostListening"))), 
               rumination~Timepoint, 
               CI = TRUE)  +
  scale_x_discrete(labels = c("Post Induction", "Post Listening")) + 
  ggplot2::scale_colour_viridis_d(labels = c("+1 SD", "Mean", "-1 SD"),
                                name = "Rumination \nScore")+
  ggplot2::ylab("Predicted Sadness Score") + 
  ggplot2::xlab("Timepoint") +
  ggplot2::theme_classic(base_size = 12, base_family = "Times New Roman") 

confirm_plot
```


## Exploratory Analysis

A new trait was added at each step
Step 1: Baseline sadness
Step 2: Use of music for regulation
Step 3: Rumination

```{r}
Nov18ExploreLong <- Nov18WorkingLong %>% 
  filter(Timepoint != "Baseline") %>% 
  left_join(dplyr::select(Nov18BasicClean, ResponseId, Baseline, musebaq, age, gender, hours.listen), by = "ResponseId") 

Step1 <- lmerTest::lmer(Sadness~ 1+Timepoint*Baseline + (1 | ResponseId), data = Nov18ExploreLong)
Step2 <- lmerTest::lmer(Sadness~ 1+Timepoint*Baseline + Timepoint*musebaq + (1 | ResponseId), data = Nov18ExploreLong)
Step3 <- lmerTest::lmer(Sadness~ 1+Timepoint*Baseline + Timepoint*musebaq +Timepoint*hours.listen + (1 | ResponseId), data = Nov18ExploreLong)
Step4 <- lmerTest::lmer(Sadness~ 1+Timepoint*Baseline + Timepoint*musebaq +Timepoint*hours.listen +Timepoint*rumination + (1 | ResponseId), data = Nov18ExploreLong)

sjPlot::tab_model(Step1, Step2, Step3, Step4, 
                  show.std = TRUE, 
                  show.est = FALSE, 
                  show.aic = TRUE, 
                  show.aicc = TRUE, 
                  show.loglik = TRUE)

anova(Step1, Step2, Step3, Step4) %>% 
  knitr::kable() %>% 
  kableExtra::kable_styling()
```

```{r}
stepback <- buildmer::buildmer(formula = Sadness~ 1+Timepoint*Baseline + Timepoint*musebaq + Timepoint*rumination + Timepoint*hours.listen + Timepoint*age + Timepoint*gender +(1 | ResponseId), 
                   data = Nov18ExploreLong, 
                   crit = "AIC", 
                   direction = "backward")

stepbackchosen <- lmerTest::lmer(formula = stepback@p[["formula"]], 
                                 data = Nov18ExploreLong)

tab_model(stepbackchosen, 
          show.std = TRUE, 
                  show.aic = TRUE)

anova(stepbackchosen, Step4)


```



