---
title: "Rumination, Emotion Induction Mechanisms and Sad Music"
author: "Joel Larwood"
output: 
  html:
    code_folding: hide
    toc: TRUE
    toc_float: TRUE
    number_sections: TRUE
---

```{r setOpts, echo=TRUE}
knitr::opts_chunk$set(autodep = TRUE, warning = FALSE, message = FALSE)

options(digits=3)
```

```{r pacakgeLoad, warnings = FALSE, message = FALSE}
library(tidyverse)
library(lmerTest)
library(buildmer)
library(psych)
library(kableExtra)
library(apa)
library(interactions)
library(corrplot)
```

The code to clean the orginal data can be seen [here]() and run with the following code chunk
```{r sourceProcess, eval = FALSE}
source(here::here("code", "RMER_November18_Process.R"))
```

The code to get the musical information can be seen [here]() and run with the following code chunk. **Be warned the script may take up to 30 minutes to complete**. The [`data`]()folder contains data files which have the lyrics as well as the sentiment metrics.

<!-- ```{r sourceMIR, eval = FALSE} -->
<!-- source(here::here("code", "RMER_November18_MIR.R")) -->
<!-- ``` -->

# Data joins 

The data from spotify and the data from self report were joined together 
```{r readData}
data <- read_rds(here::here("data", "RMER_November2018_ProcessedWide.rds")) 
```

<!-- To keep the data sets the same size NA values are dropped when NA is for c ertain variables  -->
<!-- ```{r} -->
<!-- data_dropped <- data %>%  -->
<!--   drop_na(musebaq:PostListening, rumination, BSR:Appraisal) -->

<!-- ``` -->

<!-- This resulted in 5 cases being deleted -->

# Descriptives of data

## Demographic Measures

### Age 
The mean age was `r round(mean(data$age, na.rm = TRUE), 2)` with a standard deviation of `r round(sd(data$age, na.rm = TRUE), 2)`

### Gender 
The gender counts can be seen in the table below. 

```{r Gender}
data %>% 
  group_by(gender) %>% 
  summarise(gender_count = n()) %>% 
  knitr::kable(format = "html") %>% 
  kableExtra::kable_styling()
```


## Trait measures 
1. Rumination
2. MUSEBAQ - Emotion and Cognitive regulation

```{r describeDemographics}
data %>% 
  select(rumination, musebaq) %>% 
  psych::describe() %>% 
    select(n, mean, sd, min, max) %>% 
  knitr::kable(digits =2, 
               format = "html") %>% 
  kableExtra::kable_styling()
```

Additionally the internal consistency for 
  a) rumination was good, `r round(psych::alpha(x = select(data, rrq_1:rrq_12))$total$raw_alpha, 2)`  
  b) the emotion and cognitive regulation scale of the MUSEBAQ was also good `r round(psych::alpha(x = select(data, musebaq_1:musebaq_9))$total$raw_alpha, 2)`


<!-- ## Song measures  -->
<!-- Note: The sentiment scores were calculated in the [MIR Script]() -->

<!-- ```{r describeValenceArousal} -->
<!-- data %>%  -->
<!--   select(valence, energy) %>%  -->
<!--   psych::describe() %>%  -->
<!--   select(n, mean, sd, min, max) %>%  -->
<!--   knitr::kable(digits =2, format = "html") %>%  -->
<!--   kableExtra::kable_styling() -->


<!-- data %>%  -->
<!--   ggplot2::ggplot(aes(x = valence, -->
<!--                       y = energy,  -->
<!--                       )) + -->
<!--   geom_point(size = 2, alpha = .5,  -->
<!--              aes(color = factor(bias))) + -->
<!--   scale_color_manual(values = c("yellow", "red", "green")) + -->
<!--   theme_classic() + -->
<!--   labs(color = "Bias of lyric \nsentiment count") -->

<!-- table(data$bias) %>%  -->
<!--   kable(col.names = c("Lyric sentiment bias", "Frequency")) %>%  -->
<!--   kable_styling() -->

<!-- ``` -->

# Correlation Matrix 

```{r CorMat, echo = FALSE}

apaTables::apa.cor.table(data = select(data,
                                       rumination, musebaq, Baseline, PostInduction, contains("mec")), 
                         filename = here::here("docs", "TraitCorrelations.rtf")) 

```

```{r corPlot}

M <- cor(select(data, 
                rumination, musebaq, Baseline, PostInduction, contains("mec")), 
         use = "pairwise.complete.obs")

res1 <- corrplot::cor.mtest(select(data, 
                rumination, musebaq, Baseline, PostInduction, contains("mec")), conf.level = .95)$p


shade <- corrplot::corrplot(M, 
                   type = "upper",
                   method = "shade", 
                   p.mat = res1, 
                   insig = "label_sig",
                   sig.level = c(.001, .01, .05),
                   pch.cex = .9, 
                   pch.col = "red")

num <- corrplot::corrplot(M, 
                   type = "upper",
                   method = "number", 
                   p.mat = res1, 
                   insig = "blank",
                   sig.level = .05,
                   pch.cex = .9, 
                   pch.col = "red")

```


# Manipulation Check 

```{r ManipCheck}
apa::t_apa(apa::t_test(data$PostInduction, data$Baseline, paired = TRUE), format = "markdown")
```

The induction of sadness was succesful, *t*(382) = 14.02, *p* < .001, *d* = 0.72

# Pre-to-Post testing {.tabset}

```{r reshapedata}

Nov18Long <- data %>% 
  select(ResponseId, 
         musebaq:Appraisal) %>% 
  pivot_longer(cols = PostInduction:PostListening, 
               names_to = "Timepoint", 
               names_ptypes = factor(), 
               values_to = "Sadness") %>% 
  mutate(Timepoint = fct_relevel(Timepoint, 
                                "PostInduction"))
```

## Hypothesis Test 
We predicted that sadness would decrease from pre to post listening and that rumination would not influence this. 

```{r HypothesisPrePost}
apa::t_apa(apa::t_test(data$PostListening, data$PostInduction, paired = TRUE), format = "markdown")
```

This was not the case, with sadness increasing when not accounting for rumination, *t*(382) = 6.37, *p* < .001, *d* = 0.33, and an intertaction between timepoint and rumination
```{r HypothesisTest}
PostInductionTimePoints <- lmerTest::lmer(Sadness~1 + Timepoint  + rumination + Timepoint:rumination + (1|ResponseId), data = Nov18Long)

sjPlot::tab_model(PostInductionTimePoints, 
                  show.std = TRUE, 
                  show.aic = TRUE,
                  show.df = TRUE
                  )
```

```{r PlotHypothesis}
minrum <- mean(Nov18Long$rumination, na.rm = TRUE) - sd(Nov18Long$rumination, na.rm = TRUE)
meanrum <- mean(Nov18Long$rumination, na.rm = TRUE)
plusrum <- mean(Nov18Long$rumination, na.rm = TRUE) + sd(Nov18Long$rumination, na.rm = TRUE)

confirm_plot <- emmeans::emmip(emmeans::ref_grid(PostInductionTimePoints, 
                                 list(rumination = c(plusrum, meanrum, minrum), Timepoint = c("PostInduction", "PostListening"))), 
               rumination~Timepoint, 
               CI = TRUE)  +
  scale_x_discrete(labels = c("Post Induction", "Post Listening")) + 
  ggplot2::scale_colour_viridis_d(labels = c("+1 SD", "Mean", "-1 SD"),
                                name = "Rumination \nScore")+
  ggplot2::ylab("Predicted Sadness Score") + 
  ggplot2::xlab(element_blank()) + 
  ggplot2::labs(subtitle = "Effect of rumination in planned model", hjust = 0) +
  ggplot2::theme_classic(base_size = 16, base_family = "Times New Roman") + 
  ggplot2::scale_y_continuous(limits = c(10,18))
                           

confirm_plot

```


```{r JN}
DummyLong <- Nov18Long %>% 
  mutate(Dummy = if_else(Timepoint == "PostInduction", 0, 1))

jn <- interactions::johnson_neyman(model = lmerTest::lmer(Sadness~1 + Dummy  + rumination + Dummy:rumination + (1|ResponseId), data = DummyLong), 
                             pred = "Dummy", 
                             modx = "rumination")


upperJN <- jn$bounds[[2]]
```

Johnson-Neyman intervals showed that the rumination did not predict increased sadness at post listening when scores were less that `r upperJN`

```{r JNPLot}
jn$plot
```

## Exploring the role of traits 

To explore the role of traits we did a greedy stepback regression using `buildmer`. All interactions between traits, including baseline mood (as a depression proxy), were included. 

The returned model is below
```{r traitExplore}

traitexplore <- buildmer::buildmer(formula = Sadness~ 1+Timepoint*Baseline + Timepoint*musebaq +Timepoint*rumination + (1 | ResponseId),
                                   data = Nov18Long, 
                                   direction='backward',
                                   na.action=na.exclude,
                                   control=lmerControl(optimizer='bobyqa'))@model

sjPlot::tab_model(traitexplore)
```

## Exploring the role of BRECVEMA mechanisms 

```{r BRECVEMAExplore}
BRECVEMAexplore <- buildmer::buildmer(Sadness~ 1+Timepoint*BSR +Timepoint*Entrainment + Timepoint*Contagion +Timepoint*Imagery+ Timepoint*Memory+Timepoint*Expectancy+Timepoint*Appraisal+ (1 | ResponseId), 
                                      data = Nov18Long, 
                                      direction='backward',
                                      control=lmerControl(optimizer='bobyqa'))@model

sjPlot::tab_model(BRECVEMAexplore, 
                  show.std = TRUE, 
                  pred.labels = FALSE)


```

## All predictors 
```{r allExplore, echo=FALSE}
AllExplore <- buildmer::buildmer(Sadness~ 1+Timepoint*BSR +Timepoint*Entrainment + Timepoint*Contagion +Timepoint*Imagery+ Timepoint*Memory+Timepoint*Expectancy+Timepoint*Appraisal+ 1+Timepoint*Baseline + Timepoint*musebaq +Timepoint*rumination +(1 | ResponseId), 
                                 data = Nov18Long,
                                 na.action=na.exclude,
                                 direction='backward',
                                 control=lmerControl(optimizer='bobyqa'))@model
```

```{r AllExploreVis}
sjPlot::tab_model(AllExplore)


RumExpl <- emmeans::emmip(emmeans::ref_grid(AllExplore, 
                                 list(rumination = c(plusrum, meanrum, minrum), Timepoint = c("PostInduction", "PostListening"))), 
               rumination~Timepoint, 
               CI = TRUE)  +
  scale_x_discrete(labels = c("Post Induction", "Post Listening")) + 
  ggplot2::scale_colour_viridis_d(labels = c("+1 SD", "Mean", "-1 SD"),
                                name = "Rumination \nScore")+
  ggplot2::ylab("Predicted Sadness Score") + 
  ggplot2::xlab("Timepoint") +
  scale_x_discrete(labels = c("Post Induction", "Post Listening")) + 
  ggplot2::scale_colour_viridis_d(labels = c("+1 SD", "Mean", "-1 SD"),
                                name = "Rumination \nScore")+
  ggplot2::ylab("Predicted Sadness Score") + 
  ggplot2::xlab(element_blank()) + 
  ggplot2::labs(subtitle = "Effect of rumination in exploratory model") +
  ggplot2::theme_classic(base_size = 16, base_family = "Times New Roman") + 
  ggplot2::scale_y_continuous(limits = c(10,18))

RumExpl
```

Johnson-neyman intervals for exploratory models 
```{r}

interactions::johnson_neyman(model = 
                               lmerTest::lmer(Sadness ~ 1 + Dummy + BSR + Dummy:BSR + Entrainment + Contagion + Dummy:Contagion + Imagery + Memory + Dummy:Memory + Appraisal + Dummy:Appraisal + Baseline + Dummy:Baseline + rumination + Dummy:rumination + (1 | ResponseId), 
                                              data = DummyLong),
                             pred = Dummy, 
                             modx = rumination
                             )
```

<!-- Force rumination:timepoint to remain in the model -->
<!-- ```{r ForceExplore} -->
<!-- ForceRum <- buildmer::buildmer(Sadness~ 1+Timepoint*BSR +Timepoint*Entrainment + Timepoint*Contagion +Timepoint*Imagery+ Timepoint*Memory+Timepoint*Expectancy+Timepoint*Appraisal+ 1+Timepoint*Baseline + Timepoint*musebaq +Timepoint*rumination +(1 | ResponseId),  -->
<!--                                include = ~ Timepoint*rumination, -->
<!--                                data = Nov18Long,  -->
<!--                                direction='backward', -->
<!--                                na.action=na.exclude, -->
<!--                                control=lmerControl(optimizer='bobyqa'))@model -->

<!-- sjPlot::tab_model(ForceRum) -->

<!-- ``` -->

## Compariosn of all models 

This comparison shows that the exploratory model had the best fit on both the AIC and BIC
```{r AIC}
cbind(
  AIC(PostInductionTimePoints, traitexplore, BRECVEMAexplore, AllExplore),
  BIC(PostInductionTimePoints, traitexplore, BRECVEMAexplore, AllExplore)
)[,c(1,2,4)] 


```

The table below shows the models as selected 
```{r}
sjPlot::tab_model(PostInductionTimePoints, 
                  AllExplore, 
                  show.est = TRUE, 
                  show.std = TRUE, 
                  show.fstat = TRUE, 
                  pred.labels = FALSE)
```


# Rumination across planned and stepback models 

```{r}

legend <- cowplot::get_legend(confirm_plot)

plots <- cowplot::plot_grid(confirm_plot + 
                     theme(legend.position = "none"),
                   RumExpl + theme(legend.position = "none"), 
                   nrow = 2) 

cowplot::plot_grid(plots, 
                   legend, 
                   ncol = 2, 
                   rel_widths = c(2, .8))
```

Rumination slopes
```{r}
NoMech <- emmeans::emmeans(AllExplore, 
                           ~rumination*Timepoint, 
                           at = (list(rumination = c(minrum, plusrum, meanrum),
                                      Timepoint = c("PostInduction",
                                                    "PostListening"), 
                                      Contagion = "No", 
                                      Entrainment = "No", 
                                      BSR = "No", 
                                      Memory = "No", 
                                      Imagery = "No",
                                      Appraisal = "No")))

emmeans::contrast(NoMech, 
                  "pairwise", 
                  by = "rumination")

AllMech <- emmeans::emmeans(AllExplore, 
                            ~rumination*Timepoint, 
                            at = (list(rumination = c(minrum, plusrum, meanrum),
                                       Timepoint = c("PostInduction",
                                                     "PostListening"), 
                                       Contagion = "Yes", 
                                       Entrainment = "Yes", 
                                       BSR = "Yes", 
                                       Memory = "Yes", 
                                       Imagery = "Yes",
                                       Appraisal = "Yes")))
emmeans::contrast(AllMech, 
                  "pairwise", 
                  by = c("rumination"))

ContOnly <- emmeans::emmeans(AllExplore, 
                                   ~rumination*Timepoint, 
                                   at = (list(rumination = c(minrum, plusrum, meanrum),
                                              Timepoint = c("PostListening",
                                                            "PostInduction"), 
                                              Contagion = "Yes", 
                                              Entrainment = "No", 
                                              BSR = "No", 
                                              Memory = "No", 
                                              Imagery = "No",
                                              Appraisal = "No")))
emmeans::contrast(ContOnly, 
                  "pairwise", 
                  by = c("rumination"))

ContApp <- emmeans::emmeans(AllExplore, 
                                   ~rumination*Timepoint, 
                                   at = (list(rumination = c(minrum, plusrum, meanrum),
                                              Timepoint = c("PostListening",
                                                            "PostInduction"), 
                                              Contagion = "Yes", 
                                              Entrainment = "No", 
                                              BSR = "No", 
                                              Memory = "No", 
                                              Imagery = "No",
                                              Appraisal = "Yes")))
emmeans::contrast(ContApp, 
                  "pairwise", 
                  by = c("rumination"))
```

Plot scenarios 
```{r}
NoMechPlot <- emmeans::emmip(NoMech,
                  rumination~Timepoint, 
                  CI = TRUE) + 
  ggplot2::scale_colour_viridis_d(labels = c("+1 SD", "Mean", "-1 SD"),
                                name = "Rumination \nScore")+
  ggplot2::ylab("Predicted Sadness Score") + 
  ggplot2::xlab("Timepoint") +
  ggplot2::theme_classic(base_size = 12, base_family = "Times New Roman") + 
  scale_x_discrete(labels = c("Post Induction", "Post Listening")) + 
  ggplot2::scale_colour_viridis_d(labels = c("+1 SD", "Mean", "-1 SD"),
                                name = "Rumination \nScore")+
  ggplot2::ylab("Predicted Sadness Score") + 
  ggplot2::xlab(element_blank()) + 
  ggplot2::labs(subtitle = "No mechanisms occur") +
  ggplot2::scale_y_continuous(limits = c(8,18))


AllMechPlot <- emmeans::emmip(AllMech, 
                                   rumination~Timepoint, 
                                   CI = TRUE) + 
  ggplot2::scale_colour_viridis_d(labels = c("+1 SD", "Mean", "-1 SD"),
                                name = "Rumination \nScore")+
  ggplot2::ylab("Predicted Sadness Score") + 
  ggplot2::xlab("Timepoint") +
  ggplot2::theme_classic(base_size = 12, base_family = "Times New Roman") + 
  scale_x_discrete(labels = c("Post Induction", "Post Listening")) + 
  ggplot2::scale_colour_viridis_d(labels = c("+1 SD", "Mean", "-1 SD"),
                                name = "Rumination \nScore")+
  ggplot2::ylab("Predicted Sadness Score") + 
  ggplot2::xlab(element_blank()) + 
  ggplot2::labs(subtitle = "All included mechanisms occur") +
  ggplot2::scale_y_continuous(limits = c(8,18))

ContOnlyPlot <- emmeans::emmip(ContOnly, 
                                   rumination~Timepoint, 
                                   CI = TRUE) + 
  ggplot2::scale_colour_viridis_d(labels = c("+1 SD", "Mean", "-1 SD"),
                                name = "Rumination \nScore")+
  ggplot2::ylab("Predicted Sadness Score") + 
  ggplot2::xlab("Timepoint") +
  ggplot2::theme_classic(base_size = 12, base_family = "Times New Roman") + 
  scale_x_discrete(labels = c("Post Induction", "Post Listening")) + 
  ggplot2::scale_colour_viridis_d(labels = c("+1 SD", "Mean", "-1 SD"),
                                name = "Rumination \nScore")+
  ggplot2::ylab("Predicted Sadness Score") + 
  ggplot2::xlab(element_blank()) + 
  ggplot2::labs(subtitle = "Only emotional contagion \noccurs") +
  ggplot2::scale_y_continuous(limits = c(8,18))

ContAppPlot <- emmeans::emmip(ContApp, 
                                   rumination~Timepoint, 
                                   CI = TRUE) + 
  ggplot2::scale_colour_viridis_d(labels = c("+1 SD", "Mean", "-1 SD"),
                                name = "Rumination \nScore")+
  ggplot2::ylab("Predicted Sadness Score") + 
  ggplot2::xlab("Timepoint") +
  ggplot2::theme_classic(base_size = 12, base_family = "Times New Roman") + 
  scale_x_discrete(labels = c("Post Induction", "Post Listening")) + 
  ggplot2::scale_colour_viridis_d(labels = c("+1 SD", "Mean", "-1 SD"),
                                name = "Rumination \nScore")+
  ggplot2::ylab("Predicted Sadness Score") + 
  ggplot2::xlab(element_blank()) + 
  ggplot2::labs(subtitle = "Only emotional contagion and \nappraisal occur") +
  ggplot2::scale_y_continuous(limits = c(8,18))

MechGrid <- cowplot::plot_grid(NoMechPlot + theme(legend.position = "none"), 
                               AllMechPlot + theme(legend.position = "none"), 
                               ContOnlyPlot + theme(legend.position = "none"),
                               ContAppPlot + theme(legend.position = "none")) 

MechGrid <- cowplot::plot_grid(MechGrid, 
                               legend, 
                               rel_widths = c(2, .5))

MechGrid
                               
```

