---
title: "Rumination, Emotion Induction Mechanisms and Sad Music"
author: "Joel Larwood"
output: 
  html:
    code_folding: hide
    toc: TRUE
    toc_float: TRUE
    number_sections: TRUE
---

```{r setOpts, echo=TRUE}
knitr::opts_chunk$set(autodep = TRUE, warning = FALSE, message = FALSE)

options(digits=3)
```

```{r pacakgeLoad, warnings = FALSE, message = FALSE}
library(tidyverse)
library(lmerTest)
library(buildmer)
library(psych)
library(kableExtra)
library(apa)
library(interactions)
```

The code to clean the orginal data can be seen [here]() and run with the following code chunk
```{r eval = FALSE}
source(here::here("code", "RMER_November18_Process.R"))
```

The code to get the musical information can be seen [here]() and run with the following code chunk. **Be warned the script may take up to 30 minutes to complete**. The [`data`]()folder contains data files which have the lyrics as well as the sentiment metrics. 
```{r eval = FALSE}
source(here::here("code", "RMER_November18_MIR.R"))
```

# Data joins 

The data from spotify and the data from self report were joined together 
```{r}
data <- read_rds(here::here("data", "RMER_November2018_ProcessedWide.rds")) %>% 
  left_join(read_rds(here::here("data", "RMER_November2018_Features_Sentiment.rds")), by = "ID")
```

# Descriptives of data

## Demographic Measures

### Age 
The mean age was `r round(mean(data$age, na.rm = TRUE), 2)` with a standard deviation of `r round(sd(data$age, na.rm = TRUE), 2)`

### Gender 
The gender counts can be seen in the table below. 

```{r Gender}
data %>% 
  group_by(gender) %>% 
  summarise(gender_count = n()) %>% 
  knitr::kable(format = "html") %>% 
  kableExtra::kable_styling()
```


## Trait measures 
1. Rumination
2. MUSEBAQ - Emotion and Cognitive regulation

```{r describe demographics}
data %>% 
  select(rumination, musebaq) %>% 
  psych::describe() %>% 
    select(n, mean, sd, min, max) %>% 
  knitr::kable(digits =2, 
               format = "html") %>% 
  kableExtra::kable_styling()
```

Additionally the internal consistency for 
  a) rumination was good, `r round(psych::alpha(x = select(data, rrq_1:rrq_12))$total$raw_alpha, 2)`  
  b) the emotion and cognitive regulation scale of the MUSEBAQ was also good `r round(psych::alpha(x = select(data, musebaq_1:musebaq_9))$total$raw_alpha, 2)`


## Song measures 
Note: The sentiment scores were calculated in the [MIR Script]()

```{r}
data %>% 
  select(valence, energy, ) %>% 
  psych::describe() %>% 
  select(n, mean, sd, min, max) %>% 
  knitr::kable(digits =2, format = "html") %>% 
  kableExtra::kable_styling()


data %>% 
  ggplot2::ggplot(aes(x = valence,
                      y = energy, 
                      )) +
  geom_point(size = 2, alpha = .5, 
             aes(color = factor(bias))) +
  scale_color_manual(values = c("yellow", "red", "green")) +
  theme_classic() +
  labs(color = "Bias of lyric \nsentiment count")

table(data$bias) %>% 
  kable(col.names = c("Lyric sentiment bias", "Frequency")) %>% 
  kable_styling()
  
```

# Correlation Matrix 



# Manipulation Check 

The induction of sadness was succesful `r apa::t_apa(apa::t_test(data$PostInduction, data$Baseline, paired = TRUE), format = "markdown")`

# Pre-to-Post testing {.tabset}

```{r reshapedata}

Nov18Long <- data %>% 
  select(ResponseId, 
         musebaq:Appraisal) %>% 
  pivot_longer(cols = PostInduction:PostListening, 
               names_to = "Timepoint", 
               names_ptypes = factor(), 
               values_to = "Sadness") %>% 
  mutate(Timepoint = fct_relevel(Timepoint, 
                                "PostInduction"))
```

## Hypothesis Test 
We predicted that sadness would decrease from pre to post listening and that rumination would not influence this. 

This was not the case, with sadness increasing when not accounting for rumination,`r apa::t_apa(apa::t_test(data$PostListening, data$PostInduction, paired = TRUE), format = "markdown")` , and an intertaction between timepoint and rumination
```{r HypothesisTest}
PostInductionTimePoints <- lmerTest::lmer(Sadness~1 + Timepoint  + rumination + Timepoint:rumination + (1|ResponseId), data = filter(Nov18Long, Timepoint != "Baseline"))

sjPlot::tab_model(PostInductionTimePoints, 
                  show.std = TRUE, 
                  show.aic = TRUE,
                  show.df = TRUE
                  )
```

```{r}
minrum <- mean(Nov18Long$rumination, na.rm = TRUE) - sd(Nov18Long$rumination, na.rm = TRUE)
meanrum <- mean(Nov18Long$rumination, na.rm = TRUE)
plusrum <- mean(Nov18Long$rumination, na.rm = TRUE) + sd(Nov18Long$rumination, na.rm = TRUE)

confirm_plot <- emmeans::emmip(emmeans::ref_grid(PostInductionTimePoints, 
                                 list(rumination = c(plusrum, meanrum, minrum), Timepoint = c("PostInduction", "PostListening"))), 
               rumination~Timepoint, 
               CI = TRUE)  +
  scale_x_discrete(labels = c("Post Induction", "Post Listening")) + 
  ggplot2::scale_colour_viridis_d(labels = c("+1 SD", "Mean", "-1 SD"),
                                name = "Rumination \nScore")+
  ggplot2::ylab("Predicted Sadness Score") + 
  ggplot2::xlab("Timepoint") +
  ggplot2::theme_classic(base_size = 20, base_family = "Times New Roman") 

confirm_plot

```


```{r}
emmeans::contrast(emmeans::emmeans(PostInductionTimePoints, 
                                   ~rumination*Timepoint, 
                                   at = (list(rumination = c(minrum, plusrum, meanrum), Timepoint = c("PostInduction", "PostListening")))), 
                  "pairwise", 
                  by = "rumination")
```



```{r}
DummyLong <- Nov18Long %>% 
  filter(Timepoint != "Baseline") %>% 
  mutate(Dummy = if_else(Timepoint == "PostInduction", 0, 1))

jn <- interactions::johnson_neyman(model = lmerTest::lmer(Sadness~1 + Dummy  + rumination + Dummy:rumination + (1|ResponseId), data = DummyLong), 
                             pred = "Dummy", 
                             modx = "rumination")


upperJN <- jn$bounds[[2]]
```

Johnson-Neyman intervals showed that the rumination did not predict increased sadness at post listening when scores were less that `r upperJN`

```{r}
jn$plot
```

## Exploring the role of traits 

To explore the role of traits we did a greedy stepback regression using `buildmer`. All interactions between traits, including baseline mood (as a depression proxy), were included. 

The returned model is below
```{r}

traitexplore <- buildmer::buildmer(formula = Sadness~ 1+Timepoint*Baseline + Timepoint*musebaq +Timepoint*rumination + (1 | ResponseId),
                                   data = Nov18Long, 
                                   direction='backward',
                                   control=lmerControl(optimizer='bobyqa'))@model

sjPlot::tab_model(traitexplore)

exploreplots <- sjPlot::plot_model(traitexplore, 
                   type = "int", 
                   mdrt.values = "meansd", 
                   title = "") 

cowplot::plot_grid(exploreplots[[1]], exploreplots[[2]], 
                   nrow = 2, 
                   ncol =1)

```

## Exploring the role of BRECVEMA mechanisms 

```{r}
BRECVEMAexplore <- buildmer::buildmer(Sadness~ 1+Timepoint*BSR +Timepoint*Entrainment + Timepoint*Contagion +Timepoint*Imagery+ Timepoint*Memory+Timepoint*Expectancy+Timepoint*Appraisal+ (1 | ResponseId), 
                                      data = Nov18Long, 
                                      direction='backward',
                                      control=lmerControl(optimizer='bobyqa'))@model

sjPlot::tab_model(BRECVEMAexplore, 
                  show.std = TRUE)


exploreplots <- sjPlot::plot_model(BRECVEMAexplore, 
                   type = "int", 
                   title = "") 

cowplot::plot_grid(exploreplots[[1]], exploreplots[[2]], exploreplots[[3]], exploreplots[[4]], 
                   ncol =2, 
                   nrow = 2, 
                   labels = NULL)
```

## All predictors 
```{r}
AllExplore <- buildmer::buildmer(Sadness~ 1+Timepoint*BSR +Timepoint*Entrainment + Timepoint*Contagion +Timepoint*Imagery+ Timepoint*Memory+Timepoint*Expectancy+Timepoint*Appraisal+ 1+Timepoint*Baseline + Timepoint*musebaq +Timepoint*rumination +(1 | ResponseId), 
                                 data = Nov18Long, 
                                 direction='backward',
                                 control=lmerControl(optimizer='bobyqa'))@model

sjPlot::tab_model(AllExplore)

Allexploreplots <- sjPlot::plot_model(AllExplore, 
                   type = "int", 
                   title = "") 

cowplot::plot_grid(Allexploreplots[[1]], Allexploreplots[[2]], Allexploreplots[[3]], Allexploreplots[[4]], Allexploreplots[[5]], Allexploreplots[[6]],
                   ncol =2, 
                   nrow = 3, 
                   labels = NULL)
```

## Compariosn of all models 

```{r}

```

