---
title: "Process and Describe"
author: "joellarwood"
date: "2019-12-13"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

```{r install, echo = FALSE, warnings = FALSE, message=FALSE}
library(tidyverse)
library(psych)
library(ggpubr)
library(here)
library(glue)
library(kableExtra)
library(qualtRics)

knitr::opts_chunk$set(autodep = TRUE, warnings = FALSE, message = FALSE)
 options(scipen=999, digits=3)

```


# Load in Data

```{r LoadIn}

Nov18Working <- read_rds(here::here("data", "RMER_November2018_ProcessedWide.rds"))

```


## Descriptives
```{r descriptives}
Nov18Working %>% 
  select(age, 
         rumination, 
         hours.listen,
         Baseline, 
         PostInduction, 
         PostListening) %>% 
  psych::describe() %>% 
  knitr::kable(format = "html") %>% 
  kableExtra::kable_styling()

```

## Reliabilities
```{r Nov18Workingalphas, echo = FALSE}
baseline <- psych::alpha(dplyr::select(Nov18Working, deq_1_1:deq_1_4))$total$raw_alpha
postinduction <- psych::alpha(dplyr::select(Nov18Working, deq_2_1:deq_2_4))$total$raw_alpha
postlistening <- psych::alpha(dplyr::select(Nov18Working, deq_3_1:deq_3_4))$total$raw_alpha
rumalpha <- psych::alpha(dplyr::select(Nov18Working, rrq_1:rrq_12))$total$raw_alpha
musebaqalpha<- psych::alpha(dplyr::select(Nov18Working, musebaq_1:musebaq_9))$total$raw_alpha
```

The alpha for the DEQ - Sadness at Baseline was `r baseline`

The alpha for the DEQ DEQ - Sadness at Post Induction  was `r postinduction`

The alpha for the DEQ _ Sadness at post Listening was `r postlistening`

The alpha for rumination scores was `r rumalpha`

The alpha for the cognitive and emotion regulation scale of the MUSEBAQ was `r musebaqalpha`

